---
title: "sim_analysis"
author: "Leona Odole"
date: '2022-07-15'
output: html_document
---


```{r echo=FALSE, error=FALSE}
# Load Libraries
library(tidyverse)
library(stringr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(patchwork)
```

# Data Set-Up 
Make sure to set the working directory to the proper results directory
```{r}
# Set Working Directory
setwd("~/Desktop/REU2022/pysim/honors_thesis/results3")

# List files in directory
files = list.files()

# Read in All Data
for(f in files){
  if(f == files[1]){
    data <- read_csv(f)
  }else if(str_detect(f,"pop")){
    population <- read_csv(f)
  }else{
    data <- rbind(data, read.csv(f))
  }
}
```

# Only to compare consecutive and synthetic
```{r}
consec = data %>% filter(schedule == "consecutive") %>%
  mutate(sim_day2 = ceiling(difftime(as.POSIXct(sim_day, zone == ""),as.POSIXct("2019-02-12", zone = ""), units = "day")))

synth = data %>% filter(schedule == "synth") %>%
  mutate(sim_day2 = ceiling(difftime(as.POSIXct(sim_day, zone == ""),as.POSIXct("2020-01-02", zone = ""), units = "day")))

data = rbind(synth,consec)
```


# Add relevant calculated values and join with population data
```{r}
data = data %>% 
  left_join(population) %>%
  mutate(
    pat_percentage = pat_inf / patients,
    hcws_percentage = hcws_inf /hcws,
    run = as.factor(run),
    schedule = as.factor(schedule)
  )
```

# Calculate Confidence Intervals 

$$
t = \frac{\bar{x} - \mu}{s / \sqrt{n}}
$$
Since I want a 95% confidence interval I need to find $c$ such that 
$$
P(-c \leq t \leq c) = 0.95
$$
R uses 1 sided quantile 
```{r}
n = length(unique(data$run))
c = qt(.975, df =n-1)

```

confidence intervals are defined as 
$$
\bar{x} \pm \frac{cs}{\sqrt{n}}
$$

# Visualization
In Case of Two Synthetic Facilities Use: 
```{r}
# processed_data = data %>%
#   group_by(facility, sim_day) %>%
#   summarize(hcw_inf = mean(hcws_percentage),
#             hcw_upper = mean(hcws_percentage) + c*(sd(hcws_percentage))/sqrt(n),
#             hcw_lower = mean(hcws_percentage) - c*sd(hcws_percentage)/sqrt(n),
#             pat_inf = mean(pat_percentage),
#             pat_upper = mean(pat_percentage) + c*sd(pat_percentage)/sqrt(n),
#             pat_lower = mean(pat_percentage) - c*sd(pat_percentage)/sqrt(n)
#             )
# 
# 
# #Visualization of the infections curves with 95% confidence
#  p = processed_data %>%
#   ggplot(aes(x = sim_day, color = facility)) +
#   geom_line(aes(y = hcw_inf)) +
#   scale_color_manual(values = c("#78b260","#000000")) +
#   labs(x = "Simulation Day", y = "% Healthcare Workers Infected", title = "Infection Curve Comparison in ICUs") +
#   theme_light() +
#   theme(
#         plot.title = element_text(hjust = 0.5)
#         )
#  p + geom_errorbar(aes(ymin = hcw_lower, ymax= hcw_upper))
#  p + geom_ribbon(aes(ymin = hcw_lower, ymax= hcw_upper),alpha = 0.2, linetype = 0)
# 
# 

```

In Case of Synth vs. Consecutive Comparison:
```{r}
processed_data = data %>%
  group_by(facility,schedule,sim_day2) %>%
  summarize(hcw_inf = mean(hcws_percentage),
            hcw_upper = mean(hcws_percentage) + c*(sd(hcws_percentage))/sqrt(n),
            hcw_lower = mean(hcws_percentage) - c*sd(hcws_percentage)/sqrt(n),
            pat_inf = mean(pat_percentage),
            pat_upper = mean(pat_percentage) + c*sd(pat_percentage)/sqrt(n),
            pat_lower = mean(pat_percentage) - c*sd(pat_percentage)/sqrt(n),
            hcw_incidence = mean(hcws_inf),
            hcw_inc_u = mean(hcws_inf) + c*(sd(hcws_inf))/sqrt(n),
            hcw_inc_l = mean(hcws_inf) - c*(sd(hcws_inf))/sqrt(n)
            )
processed_data$fac_sched = processed_data %>%
  with(interaction(facility,schedule))

p = processed_data %>%
  ggplot(aes(x = sim_day2, color = fac_sched)) + #9a60b2 "#005799"
  geom_line(aes(y = hcw_incidence)) +
  scale_color_manual(values = c("#78b260","#d7bfe0","#2f4a24","#9a60b2")) +
  labs(x = "Simulation Day", y = "Infection Incidence", title = "Infection Curve Comparison in ICUs", col = "Schedule Generation Type") +
  theme_light() +
  theme(
        plot.title = element_text(hjust = 0.5)
        )

p + geom_ribbon(aes(ymin = hcw_inc_l, ymax= hcw_inc_u), alpha = 0.2, linetype = 0)
p + geom_errorbar(aes(ymin = hcw_inc_l, ymax= hcw_inc_u))
p
```
# Error Comparison Between Consec and Synth
```{r}

difference_data = full_join(x = processed_data %>% filter(schedule == "consecutive") %>% select(facility , sim_day2, hcw_incidence), # filter for consecutive schedules and grab variables needed
           y = processed_data %>% filter(schedule == "synth") %>% select(facility , sim_day2, hcw_incidence), # filter for synthetic schedules and grab variables needed
           by = c('facility', 'sim_day2')) %>% # rejoin these two datasets 
   mutate(delta = abs(hcw_incidence.x - hcw_incidence.y)) %>% # create a difference column
   select(facility, sim_day2, delta)  #Select variables needed 



only21 = difference_data %>% filter(facility == "fac21") %>%
  ggplot(aes(facility,delta)) + 
  geom_boxplot() + 
  theme(
    axis.title.x = element_blank()
  ) + labs(title = "Only Facility 21")
  

side_by_side = difference_data %>% 
  ggplot(aes(facility,delta)) + 
  geom_boxplot() + 
  theme(
    axis.title.x = element_blank()
  ) + labs(title = "Both Facilities")
  

side_by_side + only21 + 
  plot_annotation(title = "Difference In Infection Incidence")

```

